Concurrent Programming in Harmony

### 2021-03-01 book/paper.tex
Latest
Fixed x[...] code generation

The stack of each thread is subdivided into two parts: the
\emph{stack trace} and the \emph{stack top}.
A stack trace is a list of methods that are being invoked.
In this case, the \texttt{implementer} method does not invoke any
other methods, and so the list is of length 1.
For each entry in the stack trace, it shows the method name and
arguments, as well as the variables of the method.
The stack top shows the values on the stack beyond the stack trace.

@@

@@

\autoref{fig:tas} goes on to implement mutual exclusion for
a set of \texttt{N} threads.
The approach is called \emph{spinlock},
\index{spinlock}%
because each thread is ``spinning'' (executing a tight loop) until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each thread $i$ is initialized to \texttt{True}.
Method \texttt{thread} demonstrates how a local variable can be declared
in Harmony using the \textbf{let} statement---the syntax is similar to
\textbf{for} statements.  \autoref{sec:vars} provides further information.
In this case $p$ contains the address of the \textit{private} entry
for the current thread.

>>>>

The stack of each thread is subdivided into two parts: the
\emph{stack trace} and the \emph{stack top}.
A stack trace is a list of methods that are being invoked.
In this case, the \texttt{incrementer} method does not invoke any
other methods, and so the list is of length 1.
For each entry in the stack trace, it shows the method name and
arguments, as well as the variables of the method.
The stack top shows the values on the stack beyond the stack trace.

@@

Finally, methods can have local variables.
Different from Python, Harmony local variables must be
explicitly bound within a scope.
You have already seen examples: the arguments to the method,
the variable \textit{result}, and the bound variable (or
variables) within a \texttt{for} statement.
The \texttt{let} statement allows declaring additional
local variables.  For example:
\texttt{let} $x = 3$: $y$ $+$$=$ $x$ adds 3 to the global variable
$y$.
See \autoref{sec:vars} for more information.

@@

\autoref{fig:tas} goes on to implement mutual exclusion for
a set of \texttt{N} threads.
The approach is called \emph{spinlock},
\index{spinlock}%
because each thread is ``spinning'' (executing a tight loop) until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each thread $i$ is initialized to \texttt{True}.
